---
title: "mod6"
author: Audrey Tjahjadi
output: html_document
---

```{r}
f<-"C:/Users/Audrey/Desktop/countries.csv"
d<-read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)  
```
```{r}
head(d)
summary(d)
names(d)
d["country"]
median(d$population, na.rm = TRUE)
```
#median of the population, use $ to pull out just the population data from the dataset
```{r}
median(d$area, na.rm = TRUE)
d$density<-(d$population/d$area)
d$density

d <- d[order(-d$density), ]
d[1:10, ]
```
#(-) before the d$density gives descending order so that greatest density comes first
```{r}
d <- d[order(d$density), ]
d[1:10, ]
```
#without the (-) the order function gives ascending order so that least density comes first
```{r}
d1<-d[order(-d$density), ]
d1[1:20, ]
```

```{r}
summary(d1)
median(d1$population, na.rm = TRUE)
median(d1$area, na.rm = TRUE)
```
```{r}
new <- d[grep("^[A-F]", d$country), ]
summary(new)
mean(new$population, na.rm = TRUE)
mean(new$area, na.rm = TRUE)

par(mfrow = c(2,3))
#makes panel of 2 rows by 3 columns of the boxplots
boxplot(d$area)
boxplot(log(d$area))

boxplot(d$population)
boxplot(log(d$population))
```
```{r}
par(mfrow = c(1,2))
hist(log(d$area,), freq = FALSE, col = "red", main = "PLOT 1", xlab = "(log)area", ylab = "density", ylim = c(0, 0.2))
hist(log(d$population,), freq = FALSE, col = "red", main = "PLOT 1", xlab = "(log)population", ylab = "density", ylim = c(0, 0.2))
```
```{r}
sort(table(d$govt_form), decreasing = TRUE)
```

#Kamilar Data
```{r}
k<-"C:/Users/Audrey/Desktop/kamilar.csv"
m<-read.csv(k, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(m)
```

```{r}
summary(m)
```

```{r}
boxplot(log(Body_mass_female_mean) ~ Family, m)
```
#using {base} R graphics

```{r}
library(ggplot2)
p <- ggplot(data = m, aes(x = Family, y = log(Body_mass_female_mean)))
p <- p + geom_boxplot()
p <- p + theme(axis.text.x = element_text(angle = 90))
p <- p + ylab("log(Female Body Mass)")
p
```
#using {ggplot} graphics
```{r}
p <- ggplot(data = m, aes(x = log(Body_mass_female_mean), y = log(MaxLongevity_m)))
p <- p + geom_point()
p <- p + geom_smooth(method = "lm")
p
```
```{r}
library(dplyr)
aggregate(m$Body_mass_female_mean ~ m$Family, FUN = "mean", na.rm = TRUE)
```
```{r}
s <- filter(m, Family == "Hominidae" & Mass_Dimorphism > 2)
head(s)
```
```{r}
s <- arrange(m, Family, Genus, Body_mass_male_mean) 
head(s)
```
# rearranging a data frame

```{r}
s <- select(m, Family, Genus, Body_mass_male_mean)  
head(s)
```
# selecting specific columns
```{r}
byFamily <- group_by(m, Family)
byFamily
```